Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-01 paper/comoving-followup.tex
words

Typically, high-order standard polynomials or Chebyshev polynomials are used to
fit for the wavelength dispersion function.
We found that using such functions can lead to vastly incorrect wavelength
values near either end of the pixel grid where the polynomial function is
un- or weakly-constrained.
We instead use a combined linear polynomial + GP to model the wavelength
dispersion.
We again use a Mat\'ern 3/2 kernel, use \lbfgsb\ optimization, and convert any
scale parameter to log-space before maximizing the log-likelihood.
\figurename~\ref{fig:wavelength-GP} shows an example of the residuals from one such fit; black points show the (pixel-centroid, wavelength) pairs with the best-fit model subtracted, and  and fit curve (darker line).
The envelope around the best-fit curve (shaded region) shows the \todo{1$\sigma$
blah blah GP...}
When the GP variance is large, the pixel-to-wavelength mapping is uncertain; we
store this variance and later use it to mask regions of the spectra with
uncertain wavelength values.
This wavelength calibration procedure produces a nightly model for the nonlinear
dispersion of wavelength as a function of pixel value for each extracted 1D
spectrum.
\figurename~\ref{fig:sample-spectra} shows a random sample of 10 source spectra
of comoving star pair members normalized to 1 at $\lambda = 5500~{\rm \AA}$ and
shifted by index for visualization.
From the appearances of these 10 alone, it seems there is a mix of metallicities
and spectral types.
Note that the spectra are not flux-calibrated, as we only care about measuring
radial velocities from this sample.

>>>>

Typically, high-order standard polynomials or Chebyshev polynomials are used to
fit for the wavelength dispersion function.
We found that using such functions can lead to vastly incorrect wavelength
values near either end of the pixel grid where the polynomial function is
un- or weakly-constrained.
We instead use a combined linear polynomial + GP to model the wavelength
dispersion.
We again use a Mat\'ern 3/2 kernel, use \lbfgsb\ optimization, and convert any
scale parameter to log-space before maximizing the log-likelihood.
\figurename~\ref{fig:wavelength-GP} shows an example of the residuals from one
such fit; black points show the (pixel-centroid, wavelength) pairs with the
best-fit model subtracted.
The envelope around zero (shaded region) shows the \todo{1$\sigma$ blah blah
GP...}
When the GP variance is large, the pixel-to-wavelength mapping is uncertain; we
store this variance and later use it to mask regions of the spectra with
uncertain wavelength values.
This wavelength calibration procedure produces a nightly model for the nonlinear
dispersion of wavelength as a function of pixel value for each extracted 1D
spectrum.
\figurename~\ref{fig:sample-spectra} shows a random sample of 10 source spectra
of comoving star pair members normalized to 1 at $\lambda = 5500~{\rm \AA}$ and
shifted by index for visualization.
From the appearances of these 10 alone, it seems there is a mix of metallicities
and spectral types.
Note that the spectra are not flux-calibrated, as we only care about measuring
radial velocities from this sample.
